Self Regulation Ontology Retest Data Report

### 2017-11-01 code/SRO_Report.Rmd
working on updating retest report

```{r warning=FALSE, message=FALSE}
workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/User_717570_workers.csv')
workers = workers %>% 
  group_by(Worker.ID) %>%
  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
  ungroup()

worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_worker_counts.json')

@@

```{r warning=FALSE, message=FALSE}
disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/discovery_completion_dates.csv', header=FALSE)
val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/validation_completion_dates.csv', header=FALSE)
test_comp_date = rbind(disc_comp_date, val_comp_date)
rm(disc_comp_date, val_comp_date)
retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_completion_dates.csv', header=FALSE)
comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
comp_dates$test_comp = as.Date(comp_dates$test_comp)
comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
```

@@

### Load time 2 data 
```{r}
retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables.csv')

retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_noDDM.csv')

retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_EZ.csv')

@@

The original cleaning procedures include three steps:  
1. Removing outliers for each variable where outliers are defined as those who are greater than 2.5 IQR from median. **This step is skipped here because removing outliers from either dataset could lead to an unnecessary increase in missing data. Since we are interested in the average distance between two measures of a metric for a given subject instead of the distance between all these metrics this seemed appropriate.**  
2. Removing correlated variables *within* a task. In creating `meaningful_variables_clean` if variables for a given task correlated >.85 only one was kept. **This step is skipped here because we want to look at the reliability of as many variables as we can.**  
3. Log transforming variables with skew. In cleaning t1 data variables that had a |skew| > 1 were log transformed and those for which skew could not be removed successfully were dropped. **Here we transform all variables that have a |skew|>1 in t1 data but variables that are not successfully transformed will be listed and not dropped.**

>>>>

```{r warning=FALSE, message=FALSE}
workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/User_717570_workers.csv')
workers = workers %>% 
  group_by(Worker.ID) %>%
  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
  ungroup()

worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/retest_worker_counts.json')

@@

```{r warning=FALSE, message=FALSE}
disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/discovery_completion_dates.csv', header=FALSE)
val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/validation_completion_dates.csv', header=FALSE)
test_comp_date = rbind(disc_comp_date, val_comp_date)
rm(disc_comp_date, val_comp_date)
retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/retest_completion_dates.csv', header=FALSE)
comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
comp_dates$test_comp = as.Date(comp_dates$test_comp)
comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
```

@@

### Load time 2 data 
```{r}
retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables.csv')

retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables_noDDM.csv')

retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables_EZ.csv')

@@

The original cleaning procedures include three steps:  
1. Removing outliers for each variable where outliers are defined as those who are greater than 2.5 IQR from median. **This step is skipped here because removing outliers from either dataset could lead to an unnecessary increase in missing data. Since we are interested in the average distance between two measures of a metric for a given subject instead of the distance between all these metrics this seemed appropriate.**  
2. Removing correlated variables *within* a task. In creating `meaningful_variables_clean` if variables for a given task correlated >.85 only one was kept. **This step is skipped here because we want to look at the reliability of as many variables as we can.**  
3. Log transforming variables with skew. In cleaning t1 data variables that had a |skew| > 1 were log transformed and those for which skew could not be removed successfully were dropped. **Here we transform all variables that have a |skew|>1 in t1 data but variables that are not successfully transformed (i.e. where the transformation has not decreased the skew below the threshold) will be listed and not dropped.**
